IFA Comparison of Noncognitive Skills \\ BCS and MCS

### 2018-04-13 codes/R/paper/cohorts_nc.Rnw
here, folder structure

<<READ, cache=FALSE >>=
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/1_load.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/2_efa.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_inv_main.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_inv_aux.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_inv_fit.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/4_scores.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/4_scores_aux.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/5_graphs.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/6_ineq.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/7_counterf.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/7_counterf_graphs.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/7_counterf_tabs.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/7_counterf_seqdec.R")

>>>>

<<READ, cache=FALSE >>=
library(here)

read_chunk(here("codes/R/1_load.R"))
read_chunk(here("codes/R/2_efa.R"))
read_chunk(here("codes/R/3_inv_main.R"))
read_chunk(here("codes/R/3_inv_aux.R"))
read_chunk(here("codes/R/3_inv_fit.R"))
read_chunk(here("codes/R/4_scores.R"))
read_chunk(here("codes/R/4_scores_aux.R"))
read_chunk(here("codes/R/5_graphs.R"))
read_chunk(here("codes/R/6_ineq.R"))
read_chunk(here("codes/R/7_counterf.R"))
read_chunk(here("codes/R/7_counterf_graphs.R"))
read_chunk(here("codes/R/7_counterf_tabs.R"))
read_chunk(here("codes/R/7_counterf_seqdec.R"))
